Food-web structure, stochasticity and response diversity drive temporal community stability in complex communities

### 2024-03-05 _targets.Rmd
Update SEM figures

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra"))
# Load custom functions
lapply(list.files(here::here("R"), full.names = TRUE), source)
```

@@

```{targets raw_sim}
list(
  tar_target(sim_fw_file, here::here("data", "sim_fw"), format = "file"),
  tar_target(sim_fw, {
    x <- readRDS(sim_fw_file)
    x %>%
      mutate(resp_div = 1 - rho)
  }),
  tar_target(sim_param, readRDS(here::here("data", "sim_param_d2"))),
  tar_target(sim_fw_df, as.data.frame(sim_fw)),
  tar_target(sim_fw_cons, readRDS(here::here("data", "sim_fw_cons"))),
  tar_target(sim_fw_cons_df, as.data.frame(sim_fw_cons))
  )
```

@@

```{targets simplified-sem}
list(
  tar_target(sem_simplified_model_list,
    list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
      richness = lm(richness ~ ct + S, sim_fw_sem),
      #max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_sem),
      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
      avg_omnivory = lm(avg_omnivory ~ ct + S + Z, sim_fw_sem),
      avg_int_strength = lm(avg_int_strength ~ ct + S + Z, sim_fw_sem),
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_sem),
      sae_total = lm(sae_total ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h, sim_fw_sem),
      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + resp_div, sim_fw_sem),
      async = lm(async ~ sae_total + cpe, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
    ),
  tar_target(sem_simplified, {
    ti <- as.psem(sem_simplified_model_list)
    update(ti, avg_omnivory %~~% w_avg_tlvl)
    }
    ),
  tar_target(sem_simplified_coeff, {
    ti <- summary(sem_simplified)$coefficients[, c(1, 2, 8, 9)]
    colnames(ti)[4] <- "Signif"
    ti
    }),
  tar_target(sem_simplified_collinearity,
    map_dfr(setNames(sem_simplified_model_list, names(sem_simplified_model_list)),
      performance::check_collinearity,
      .id = "response") %>%
    as_tibble),
  tar_target(sem_simplified_rsquared,
    map_dfr(sem_simplified_model_list, rsquared) %>%
      mutate(
      Response = var_replacement()[Response],
      R.squared = round(R.squared, 2)
      ) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_simplified_vif,
    sem_simplified_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term],
        VIF = round(VIF, 2),
        SE_factor = round(SE_factor, 2)
        ) %>%
        rename(Response = response)
    ),
  tar_target(tab_sem_simplified_rsquared,
    sem_simplified_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  ),
  tar_target(sem_simplified_eff_file, here::here("data", "sem_simplified_eff"), format = "file"),
  tar_target(sem_simplified_eff, {
    readRDS(sem_simplified_eff_file)
    #semEff(sem_simplified, ci.type = "perc", R = 10, seed = 13, parallel = "no", data = sim_fw_sem)
    }
    ),
  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff))
)
```

@@

  tar_target(fix_fw_stab, fixef(model_fw_stab)$cond),
  tar_target(fix_fw_stab_comp,

@@

          coeff = fix_fw_stab,

@@

    fix_fw_stab_comp %>%

@@

          response = fix_fw_stab_comp$response,

@@

```{targets sem_tot_predictor, tar_simple = TRUE}
c("richness", "avg_int_strength", "w_avg_tlvl", "ct_alive", "Z", "h",
  "resp_div", "env_stoch")
```

```{targets plot-sem-tot}
list(
  tar_target(p_sem_tot_stab,
    sem_simplified_eff_tab %>%
      filter(effect_type == "total") %>%
      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
      filter(predictor %in% sem_tot_predictor()) %>%
      mutate(
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE)
        ) %>%
      ggplot(aes(
          y = predictor,
          x = effect,
          color = response,
          alpha = response,
          ymin = lower_ci,
          ymax = upper_ci)
        ) +
      geom_pointrange() +
      scale_colour_manual(values = stab_color()) +
      scale_alpha_manual(values = stab_alpha()) +
      #  geom_hline(yintercept = 0, linetype = "dashed") +
      geom_vline(xintercept = 0, linetype = "dashed") +
      #facet_grid(cols = vars(response)) +
      labs(
        x = "Total standardised effects",
        color = "Stability component",
        alpha = "Stability component"
        ) +
      theme_bw() +
      theme(
        axis.title.y = element_blank(),
        #legend.justification = "right",
        legend.position = "bottom") +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
        ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top")
      )
    ),
  tar_target(p_sem_tot_stab_leg,
    plot_grid(
      print(p_sem_tot_stab +
        theme(
          legend.position = "none",
        )
        ),
      get_legend(p_sem_tot_stab),
      nrow = 2,
      rel_heights = c(1, .05)
      )
  )
)
```

@@

@@

```{r}
sem_file <- here("report", "figures", "sem_stab_simplified.pdf")
p_sem <- ggdraw() +
  draw_image(magick::image_read_pdf(sem_file, density = 600),
    x = 0, y = 0,
    width = 1, height = 1,
    hjust = 0, halign = 0, valign = 0
  )
p_sem_tot <- plot_grid(
  p_sem, p_sem_simplified_bivariate_relations,
  nrow = 2, rel_heights = c(.6, 1),
  labels = "auto"
)
```

```{r fig-sem}
ggsave_multiple(
  paste0("p_sem_tot", c(".jpg", ".png", ".pdf")),
  plot = p_sem_tot,
  path = here::here("report", "figures"),
  scale = 2.4,
  dpi = 400,
  width = 80,
  height = 80 * 1.6,
  units = "mm")
```

@@

```{r}
bivariate_rel_file <- here("report", "figures", "p_sem_simplified_bivariate_relations.jpg")
p_bivariate_rel <- ggdraw() +
  draw_image(magick::image_read(bivariate_rel_file, density = 300),
    x = 0, y = 0,
    width = 1, height = 1,
    hjust = 0, halign = 0, valign = 0
  )

p_sem_fig <- plot_grid(
  p_sem, p_bivariate_rel,
  print(
    tar_read(p_sem_tot_stab) +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
      ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top"),

      )
    ),
  nrow = 3, rel_heights = c(.7, 1, .6),
  labels = "auto"
)

p_sem_fig <- plot_grid(p_sem,
  print(
    tar_read(p_sem_tot_stab) +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
      ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top"),

      )
    ),
  p_bivariate_rel,
  NULL,
  nrow = 2, rel_heights = c(.7, 1),
  labels = c("a", "b", "c", ""),
  align = "h", axis = "tblr"
)
ggsave_multiple(
  paste0("p_sem_fig", c(".png", ".pdf")),
  plot = p_sem_fig,
  path = here::here("report", "figures"),
  scale = 3.4,
  dpi = 400,
  width = 80,
  height = 80 * .8,
  units = "mm")
```

```{r}
tar_load(fix_fw_stab)
tar_load(fix_fw_stab_comp)
tar_load(pred_stab_comp_rho)
```

@@

```{r}
tar_load(fix_fw_stab)
```
```{r}
tar_load(pred_stab_comp_resp_div)
```

>>>>

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra"))
# Load custom functions
lapply(list.files(here::here("R"), full.names = TRUE), source)
map_tibble <- tibble::tibble(
  names = c("no_rerun", "non_allo_no_rerun", "rerun", "no_rerun_short",
  "no_rerun_no_disconnected")
    )
```

@@

```{targets raw_sim}
list(
  tar_target(sim_fw, sim_fw_rerun),
  tar_target(sim_param, readRDS(here::here("data", "sim_param_d2"))),
  tar_target(sim_fw_df, as.data.frame(sim_fw))
  )
```

@@

```{targets all-analysis}
library(tarchetypes)
tar_map(
  values = map_tibble,
  names = names,
  tar_target(sim_files, here::here("data", paste0("sim_fw_", names)), format = "file"),
  tar_target(sim_fw, readRDS(sim_files)),
  tar_target(sem_simplified_eff_file, here::here("data", paste0("sem_simplified_eff_", names)), format = "file"),
  tar_target(sem_simplified_eff, { readRDS(sem_simplified_eff_file) }),
  tar_target(sem_simplified_collinearity_file, here::here("data", paste0("sem_simplified_collinearity_", names)), format = "file"),
  tar_target(sem_simplified_collinearity, { readRDS(sem_simplified_collinearity_file) }),
  tar_target(sem_simplified_rsquared_file, here::here("data", paste0("sem_simplified_rsquared_", names)), format = "file"),
  tar_target(sem_simplified_rsquared, { readRDS(sem_simplified_rsquared_file) }),
  tar_target(sem_simplified_eff_tab, from_semEff_to_table(sem_simplified_eff))
)
```

```{targets group-all-analysis}
list(
  tar_target(sem_simplified_tot,
    tibble(
      sim_type = c(
        "no_rerun",
        "non_allo_no_rerun",
        "rerun",
        "no_rerun_short",
        "no_rerun_no_disconnected"),
      eff = list(
        sem_simplified_eff_tab_no_rerun,
        sem_simplified_eff_tab_non_allo_no_rerun,
        sem_simplified_eff_tab_rerun,
        sem_simplified_eff_tab_no_rerun_short,
        sem_simplified_eff_tab_no_rerun_no_disconnected
        ),
      rsq = list(
        sem_simplified_rsquared_no_rerun,
        sem_simplified_rsquared_non_allo_no_rerun,
        sem_simplified_rsquared_rerun,
        sem_simplified_rsquared_no_rerun_short,
        sem_simplified_rsquared_no_rerun_no_disconnected
        ),
      collinearity = list(
        sem_simplified_collinearity_no_rerun,
        sem_simplified_collinearity_non_allo_no_rerun,
        sem_simplified_collinearity_rerun,
        sem_simplified_collinearity_no_rerun_short,
        sem_simplified_collinearity_no_rerun_no_disconnected
        ),
    )
  ),
  tar_target(sem_simplified_eff_tab_tot,
    sem_simplified_tot %>%
      select(sim_type, eff) %>%
      unnest(cols = eff)),
  tar_target(p_sem_simplified_eff_tab_tot,
    sem_simplified_eff_tab_tot %>%
      filter(effect_type == "total") %>%
      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
      filter(predictor %in% sem_tot_predictor()) %>%
      mutate(
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE),
        sim_type = recode_factor(sim_type, !!!sim_type_replacement(), .ordered = TRUE)
        ) %>%
      ggplot(aes(
          y = predictor,
          x = effect,
          color = response,
          shape = sim_type
        )
        ) +
      geom_point(alpha = .5) +
      scale_colour_manual(values = stab_color()) +
      scale_alpha_manual(values = stab_alpha()) +
      #  geom_hline(yintercept = 0, linetype = "dashed") +
      geom_vline(xintercept = 0, linetype = "dashed") +
      facet_grid(cols = vars(response)) +
      labs(
        x = "Total standardised effects",
        color = "Stability component",
        alpha = "Stability component"
        ) +
      theme_bw() +
      theme(
        axis.title.y = element_blank(),
        #legend.justification = "right",
        legend.position = "bottom") +
      guides(
        color = FALSE
        ) +
      theme(
        legend.title = element_blank(),
        legend.position = "bottom",
        legend.justification = c("left", "top")
      )
  )
)
```

```{targets simplified-sem}
list(
  tar_target(sem_simplified_model_list,
    list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
      richness = lm(richness ~ ct + S, sim_fw_sem),
      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
      avg_omnivory = lm(avg_omnivory ~ ct + S + Z, sim_fw_sem),
      avg_int_strength = lm(avg_int_strength ~ ct + S + Z, sim_fw_sem),
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_sem),
      #sae_even = lm(sae_even ~ richness, sim_fw_sem),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h, sim_fw_sem),
      sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + resp_div, sim_fw_sem),
      async = lm(async ~ sae_total + cpe, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
    ),
  tar_target(sem_simplified, {
    ti <- as.psem(sem_simplified_model_list)
    update(ti, avg_omnivory %~~% w_avg_tlvl)
    }
    ),
  tar_target(sem_main_text_model_list,
    list(
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch, sim_fw_sem),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive, sim_fw_sem),
      sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
      cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div, sim_fw_sem),
      async = lm(async ~ sae_total + cpe, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
  ),
  tar_target(sem_main_text, {
    ti <- as.psem(sem_main_text_model_list)
    #update(ti, avg_omnivory %~~% w_avg_tlvl)
    }
    ),
  tar_target(sem_simplified_collinearity,
    sem_simplified_collinearity_no_rerun
    ),
  tar_target(sem_simplified_rsquared,
    sem_simplified_rsquared_no_rerun %>%
      mutate(
      Response = var_replacement()[Response],
      R.squared = round(R.squared, 2)
      ) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_simplified_vif,
    sem_simplified_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term],
        VIF = round(VIF, 2),
        SE_factor = round(SE_factor, 2)
        ) %>%
        rename(Response = response)
    ),
  tar_target(tab_sem_simplified_rsquared,
    sem_simplified_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  ),
  tar_target(sem_simplified_eff_tab, sem_simplified_eff_tab_no_rerun)
)
```

```{r, eval = FALSE}
tar_load(sem_main_text)
m <- list(
  pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch, sim_fw_sem),
  evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive, sim_fw_sem),
  sae_total = lm(sae_total ~ richness + evenness_sae, sim_fw_sem),
  cpe = lm(cpe ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + resp_div, sim_fw_sem),
  async = lm(async ~ sae_total + cpe, sim_fw_sem),
  stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
)
ti <- as.psem(m)
update(ti, avg_omnivory %~~% w_avg_tlvl)
summary(ti)
```

@@

  tar_target(fixed_effect_fw_stab, fixef(model_fw_stab)$cond),
  tar_target(fixed_effect_fw_stab_comp,

@@

          coeff = fixed_effect_fw_stab,

@@

    fixed_effect_fw_stab_comp %>%

@@

          response = fixed_effect_fw_stab_comp$response,

@@

```{r, eval = FALSE}
tar_load(sem_simplified_tot)
sem_simplified_tot %>%
  select(sim_type, collinearity) %>%
  unnest(cols = c(collinearity)) %>%
  group_by(sim_type) %>%
  summarise(
    med = median(VIF),
    max = max(VIF)
  )
```

```{targets plot-sem-tot}
list(
  tar_target(p_sem_tot_stab,
    sem_simplified_eff_tab_no_rerun %>%
      filter(effect_type == "total") %>%
      filter(response %in% c("async", "pop_stab", "stab_com")) %>%
      filter(predictor %in% sem_tot_predictor()) %>%
      mutate(
        response = recode_factor(response, !!!var_replacement(), .ordered = TRUE),
        predictor = recode_factor(predictor, !!!var_replacement()[rev(sem_tot_predictor())], .ordered = TRUE)
        ) %>%
      ggplot(aes(
          y = predictor,
          x = effect,
          color = response,
          alpha = response,
          ymin = lower_ci,
          ymax = upper_ci)
        ) +
      geom_pointrange() +
      scale_colour_manual(values = stab_color()) +
      scale_alpha_manual(values = stab_alpha()) +
      #  geom_hline(yintercept = 0, linetype = "dashed") +
      geom_vline(xintercept = 0, linetype = "dashed") +
      #facet_grid(cols = vars(response)) +
      labs(
        x = "Total standardised effects",
        color = "Stability component",
        alpha = "Stability component"
        ) +
      theme_bw() +
      theme(
        axis.title.y = element_blank(),
        #legend.justification = "right",
        legend.position = "bottom") +
      guides(
        color = guide_legend(override.aes = list(linetype = 0, alpha = 1))
        ) +
      theme(
        legend.title = element_blank(),
        legend.position = c(.005, .995),
        legend.justification = c("left", "top")
      )
    ),
  tar_target(p_sem_tot_stab_leg,
    plot_grid(
      print(p_sem_tot_stab +
        theme(
          legend.position = "none",
        )
        ),
      get_legend(p_sem_tot_stab),
      nrow = 2,
      rel_heights = c(1, .05)
      )
  ),
  tar_target(sem_file, here("report", "figures", "sem_stab_simplified_simple.pdf"), format = "file"),
  tar_target(p_sem,
    ggdraw() +
      draw_image(magick::image_read_pdf(sem_file, density = 600),
        x = 0, y = 0,
        width = 1, height = 1,
        hjust = 0, halign = 0, valign = 0
      )
  ),
  tar_target(p_sem_fig,
    plot_grid(
      p_sem,
      print(
        tar_read(p_sem_tot_stab) +
          guides(
            color = guide_legend(override.aes = list(linetype = 0, alpha = 1)),
            y = "none",
            y.sec = "axis"
          ) +
          theme(
            legend.title = element_blank(),
            legend.position = c(.005, .995),
            legend.justification = c("left", "top"),

          )
        ),
      nrow = 2, rel_heights = c(1, .8),
      labels = "auto"
  )

@@

```{r, eval=FALSE}
tar_load(sem_simplified_eff_tab_no_rerun_short)
sem_simplified_eff_tab_rerun %>%
  filter(
    effect_type == "direct",
    predictor %in% c(sem_tot_predictor(), "async", "stab_com", "sae_total", "cpe", "evenness_sae", "sae_even")
    ) %>%
select(response, predictor, effect) %>%
filter(abs(effect) > .05) %>%
mutate(effect = round(effect, 2))
```

@@

```{r}
p_sem_tot <- plot_grid(
  p_sem, p_sem_simplified_bivariate_relations,
  nrow = 2, rel_heights = c(.6, 1),
  labels = "auto"
)
```

```{r fig-sem}
ggsave_multiple(
  paste0("p_sem_tot", c(".jpg", ".png", ".pdf")),
  plot = p_sem_tot,
  path = here::here("report", "figures"),
  scale = 2.4,
  dpi = 400,
  width = 80,
  height = 80 * 1.6,
  units = "mm")
```
```{r fig-sem-tot-sensibility}
ggsave_multiple(
  paste0("p_sem_simplified_eff_tab_tot", c(".jpg", ".png", ".pdf")),
  plot = tar_read(p_sem_simplified_eff_tab_tot),
  path = here::here("report", "figures"),
  scale = 2.4,
  dpi = 400,
  width = 80,
  height = 80 * .5,
  units = "mm")
```

@@

```{r, eval = FALSE}
bivariate_rel_file <- here("report", "figures", "p_sem_simplified_bivariate_relations.jpg")
p_bivariate_rel <- ggdraw() +
  draw_image(magick::image_read(bivariate_rel_file, density = 300),
    x = 0, y = 0,
    width = 1, height = 1,
    hjust = 0, halign = 0, valign = 0
  )
```

```{r}

ggsave_multiple(
  paste0("p_sem_fig", c(".png", ".pdf")),
  plot = tar_read(p_sem_fig),
  path = here::here("report", "figures"),
  scale = 3.4,
  dpi = 400,
  width = 80,
  height = 80 * 1,
  units = "mm")
```

```{r}
tar_load(fixed_effect_fw_stab)
tar_load(fixed_effect_fw_stab_comp)
tar_load(pred_stab_comp_rho)
```

@@

```{r}
tar_load(fixed_effect_fw_stab)
```
```{r}
tar_load(pred_stab_comp_resp_div)
```

### 2024-03-05 paper/manuscript.Rmd
Update SEM figures

---
title: Food-web structure, stochasticity and response diversity drive temporal community stability in complex communities
author: "Alain Danet, (Sonia Kéfi, Thomas F Johnson), Andrew P. Beckerman"
date: ""
output:
  officedown::rdocx_document:
    number_sections: false
  bookdown::pdf_document2:
    latex_engine: xelatex
    keep_tex: true
    spacing: double
    number_sections: false
always_allow_html: true
bibliography: references.bib
link-citations: true
csl: ecology-letters.csl
toc: false
linestretch: 2.0
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{hyperref}
  - \hypersetup{backref=true}
  - \usepackage{setspace}\doublespacing
---

@@

```{r}
tar_load(c(sem_eff_tab, sem_simplified_eff_tab))

@@

rvr <- get_eff(y = "cpe_env", x = "richness", tab = sem_eff_tab)
rvd <- get_eff(y = "cpe_env", x = "resp_div", tab = sem_eff_tab)
```
```{r, eval = FALSE}
sem_simplified_eff_tab %>%
  filter(abs(effect) > .1, effect_type == "direct")
```

>>>>

---
title: Food-web structure, stochasticity and response diversity drive temporal community stability in complex communities
author: "Alain Danet, (Sonia Kéfi, Thomas F Johnson), Andrew P. Beckerman"
date: ""
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    keep_tex: true
    spacing: double
    number_sections: false
  officedown::rdocx_document:
    number_sections: false
always_allow_html: true
bibliography: references.bib
link-citations: true
csl: ecology-letters.csl
toc: false
linestretch: 2.0
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \usepackage{hyperref}
  - \hypersetup{backref=true}
  - \usepackage{setspace}\doublespacing
---

@@

```{r}
tar_load(c(sem_eff_tab, sem_simplified_eff_tab))
#TODO: change for main text SEM, other SEM in appendix

@@

rvr <- get_eff(y = "cpe_env", x = "richness", tab = sem_eff_tab)
rvd <- get_eff(y = "cpe_env", x = "resp_div", tab = sem_eff_tab)
```
```{r, eval = FALSE}
tar_load(c(sem_main_text, sem_simplified))
get_coeff_psem <- function(x = NULL) {
  ti <- summary(x)$coefficients
  ti[[9]] <- NULL
  janitor::clean_names(ti)
}

ti <- get_coeff_psem(sem_main_text)
ti %>%
  filter(abs(std_estimate) > .05) %>%
  select(response, predictor, std_estimate) %>%
  mutate(std_estimate = round(std_estimate, 1))
to <- get_coeff_psem(sem_simplified)
to %>%
  filter(
    abs(std_estimate) > .05,
    predictor %in% c(
      "env_stoch", "resp_div", "ct_alive", "avg_int_strength", "w_avg_tlvl", "richness",
      "sae_total", "evenness_sae", "cpe", "pop_stab", "async", "stab_com"
    )) %>%
  select(response, predictor, std_estimate) %>%
  mutate(std_estimate = round(std_estimate, 1))
```
